### 2017-12-11 submission/manuscript.Rmd
add supplemental tables and more pvslues to first section results

# Read in fecal sample number of OTU results
fs_anova_summary <- read_csv("../data/process/tables/fecal_overall_anova_results.csv")
fs_tukey_summary <- read_csv("../data/process/tables/fecal_overall_tukey_results.csv")

@@

***The Number of OTUs is Dependent on HiFi Taq Used:***
After normalization by individual, for each cycle number, we observed that for fecal samples the number of OTUs identified was dependent upon the HiFi Taq used and this difference increased as the depth of sub-sampling increased [Figure 1]. Lower cycle numbers (15-25) resulted in less differences between Taq while cycle numbers of 30 and 35 had larger clearer defined differences [Figure 1]. Generally, the lowest number of OTUs identified was from Accuprime^TM^ while the highest was from Platinum [Figure 1]. This Taq dependent difference in the number of OTUs was also observed in the mock community samples with the same Taq polymerases being high (Platinum) and low (Accuprime) respectively [Figure 2].

>>>>

# Read in fecal sample number of OTU results
fs_anova_summary <- as.data.frame(read_csv("../data/process/tables/fecal_overall_anova_results.csv"))
fs_tukey_summary <- as.data.frame(read_csv("../data/process/tables/fecal_overall_tukey_results.csv")) %>% 
  rename(padj = `p adj`)

@@

***The Number of OTUs is Dependent on HiFi Taq Used:***
After normalization by individual, for each cycle number, we observed that for fecal samples the number of OTUs identified was dependent upon the HiFi Taq used and this difference increased as the depth of sub-sampling increased [Figure 1]. Lower cycle numbers (15-20) resulted in less differences between Taq while cycle numbers of 25, 30, and 35 had larger clearer defined differences [Figure 1]. Only 35 cycles had HiFi Taq differences that were significantly different at all sub-sampling levels (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. At sub-sampling depth of 5000 or higher 25 and 30 cycles had HiFi Taq differences (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Using a Tukey post-hoc test only at 35 cycles were significant differences found to be mainly driven by Platinum being different than all other Taq across sub-sampling depth (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2]. Across sub-sampling depth and cycle number the lowest number of OTUs identified was generally from Accuprime^TM^ while the highest was from Platinum [Figure 1]. This Taq dependent difference in the number of OTUs was also observed in the mock community samples with the same Taq polymerases being high (Platinum) and low (Accuprime) respectively [Figure 2].

### 2017-12-11 submission/manuscript.tex
add supplemental tables and more pvslues to first section results

\textbf{\emph{The Number of OTUs is Dependent on HiFi Taq Used:}} After
normalization by individual, for each cycle number, we observed that for
fecal samples the number of OTUs identified was dependent upon the HiFi
Taq used and this difference increased as the depth of sub-sampling
increased {[}Figure 1{]}. Lower cycle numbers (15-20) resulted in less
differences between Taq while cycle numbers of 25, 30, and 35 had larger
clearer defined differences {[}Figure 1{]}. Only 35 cycles had HiFi Taq
differences that were significantly different at all sub-sampling levels
(P-value \textless{} 0.0001). At sub-sampling depth of 5000 or higher 25
and 30 cycles had HiFi Taq differences (P-value \textless{} 0.05).
Generally, the lowest number of OTUs identified was from
Accuprime\textsuperscript{TM} while the highest was from Platinum
{[}Figure 1{]}. This Taq dependent difference in the number of OTUs was
also observed in the mock community samples with the same Taq
polymerases being high (Platinum) and low (Accuprime) respectively
{[}Figure 2{]}.

>>>>

\textbf{\emph{The Number of OTUs is Dependent on HiFi Taq Used:}} After
normalization by individual, for each cycle number, we observed that for
fecal samples the number of OTUs identified was dependent upon the HiFi
Taq used and this difference increased as the depth of sub-sampling
increased {[}Figure 1{]}. Lower cycle numbers (15-20) resulted in less
differences between Taq while cycle numbers of 25, 30, and 35 had larger
clearer defined differences {[}Figure 1{]}. Only 35 cycles had HiFi Taq
differences that were significantly different at all sub-sampling levels
(P-value \textless{} 0.0001) {[}Table S1{]}. At sub-sampling depth of
5000 or higher 25 and 30 cycles had HiFi Taq differences (P-value
\textless{} 0.05) {[}Table S1{]}. Using a Tukey post-hoc test only at 35
cycles were significant differences found to be mainly driven by
Platinum being different than all other Taq across sub-sampling depth
(P-value \textless{} 0.05) {[}Table S2{]}. Across sub-sampling depth and
cycle number the lowest number of OTUs identified was generally from
Accuprime\textsuperscript{TM} while the highest was from Platinum
{[}Figure 1{]}. This Taq dependent difference in the number of OTUs was
also observed in the mock community samples with the same Taq
polymerases being high (Platinum) and low (Accuprime) respectively
{[}Figure 2{]}.
